Halo alignments with large scale tidal and velocity fields

### 2013-02-19 paper/main.tex
added sections

\begin{figure}
\includegraphics[width=0.50\textwidth]{../plots/JT256.ps}
\caption{
}
\label{fig:JT256}
\end{figure}

>>>>

\section{Results}

\subsection{Volume and Mass filling fractions}

\subsection{Interweb Alignment}
... We compute the pair-wise allignment between the eigenvectors in
the two web finders.

... We also compute the alignment between the eigenvectors in cells
occupied by dark matter halos. This will be a key element in the
interpretation of the results for halo-based allignments in the next
sections: shape, angular momentum and peculiar velocities.

\subsection{Shape Alignment}
\begin{figure}
\includegraphics[width=0.50\textwidth]{../plots/JT256.ps}
\caption{
}
\label{fig:JT256}
\end{figure}

\subsection{Angular Momentum Alignment}

\subsection{Peculiar velocity Alignment}
